### 2023-05-29 application.tex
up

\begin{proof}
The reachability relation of integer $d$-VASS is definable by a sentence in Presburger in $\mathbb{Z}^d$ hence	$\Bad \subseteq \pred^*(\Safe)$ is decidable when $\Safe$ and $\Bad$ are semilinear sets. \alain{à faire}	
%		Recall that reachability is NP-complete for integer VASS. 
\mathieu{Comparé à la preuve précédente, il faut vérifier que le Home space problem est décidable dans les $\mathbb{Z}$-VASS}
\mathieu{Proposition 2, Proposition 3 dans [9] valent aussi bien pour les VASS que les 
 $\mathbb{Z}$-VASS à mon sens}
 \mathieu{Pour le Lemma 4, par contre, c'est peut-être moins évident. DC (can decrease the token) et NDC (cannot decrease the token) sont plus difficile à calculer (par exemple, MIN(DC) n'est pas calculable).}
\end{proof}

>>>>

\begin{proof}
The reachability relation of integer $d$-VASS is definable by a sentence in Presburger in $\mathbb{Z}^d$ hence	$\Bad \subseteq \pred^*(\Safe)$ is decidable when $\Safe$ and $\Bad$ are semilinear sets.
% For Z-VAS we observe that we are asking for inclusion between linear sets. 
% Again let us without loss of generality hence let us consider only the case when $\Safe$ is semilinear and $\Bad = S \setminus \Safe$ is semilinear too.
\mathieu{Expliciter davantage la preuve ? $\pred^*(\Safe)$ semilinéaire car définissable en Presburger ? Puis inclusion de semilinéaires décidables.}
\end{proof}
